---
title: "St. Louis R Users Workshop"
date: "August 7, 2019" 
output: html_document
---

```{r}
# PROLOG   ################################################################

# PROJECT: NAME OF PROJECT HERE
# PURPOSE: MAJOR POINT(S) OF WHAT I AM DOING WITH THE DATA HERE
# DIR:     list directory(-ies) for files here
# DATA:    list dataset file names/availability here, e.g.,
#          filename.correctextention 
#          somewebaddress.com 
# AUTHOR:  AUTHOR NAME(S) 
# CREATED: MONTH dd, YEAR 
# LATEST:  MONTH dd, YEAR 
# NOTES:   indent all additional lines under each heading, 
#          & use the apostrophe hashmark bookends that appear  
#          KEEP PURPOSE, AUTHOR, CREATED & LATEST ENTRIES IN UPPER CASE, 
#          with appropriate case for DIR & DATA, lower case for notes 
#          If multiple lines become too much, 
#          simplify and write code book and readme. 

# PROLOG   ###############################################################
```

# Data importing

Code used to import and save the data described in the table from the internet (this takes a while):

```{r}
# open the haven package to read an xpt
library(package = "haven")

# create a temporary file to store the zipped file
# before you open it
temp <- tempfile(fileext = ".zip")

# use download.file to put the zipped file in the temp file
# this will take a couple of minutes depending on computer speed
download.file(url = "http://www.cdc.gov/brfss/annual_data/2014/files/LLCP2014XPT.zip",
              destfile = temp)

# unzip it and read it
brfss.2014 <- read_xpt(file = temp)

# save it to data folder
write.csv(x = brfss.2014, file = "data/brfss_2014.csv", row.names = FALSE)
```

Load libraries and open saved data:

```{r}
# open tidyverse for data management
library(package = "tidyverse") 

# open tableone for making a table
library(package = "tableone")

# import data 
brfss.2014 <- read.csv(file = "data/brfss_2014.csv")
```

This is a massive data set! Luckily, they document it really well in the [codebook](https://www.cdc.gov/brfss/annual_data/2014/pdf/CODEBOOK14_LLCP.pdf). 

# Data selection 

Use `select()` in the `tidyverse` to select a subset of the variables for the table. Incude the `HADMAM` variable for reasons we will discover later. 

```{r}
# get a subset of variables 
brfss.2014.small <- brfss.2014 %>%
  select(TRNSGNDR, X_AGEG5YR, X_RACE, X_INCOMG,
         X_EDUCAG, HLTHPLN1, HADMAM)

# Take a quick look
summary(object = brfss.2014.small)
```

The table does not include all 464,664 people in the data set. Reading through the paper and looking at the table you'd find that the table includes: 

- Three transgender statuses 
- Age groups for people between 40 and 74 years old 
- People who **responded** to the mammogram question 

Look in the codebook to see how these things are coded: 

- `TRNSGNDR` coded as 1, 2, or 3 (codebook page 83) 
- `X_AGEG5YR` coded as categories 5 to 11 (codebook page 108) 
- `HADMAM` response is *not BLANK* (codebook page 37) 

```{r}
# select variables and filter cases 
brfss.2014.small <- brfss.2014 %>% 
  select(TRNSGNDR, X_AGEG5YR, X_RACE, X_INCOMG,
         X_EDUCAG, HLTHPLN1, HADMAM) %>%
  filter(TRNSGNDR >= 1 & TRNSGNDR <= 3) %>%
  filter(X_AGEG5YR >= 5 & X_AGEG5YR <= 11) %>% 
  filter(!is.na(HADMAM))

# check data set
summary(object = brfss.2014.small)
```

# Data cleaning & management

- We have the variables and cases we need for the table in the `brfss.2014.small` data frame 
- Now we clean the data 
- Start with adding labels to `TRNSGNDR` using `mutate()` and `recode_factor()` (see codebook page 83 for variable labels)

```{r}
# recode TRNSGNDR
brfss.clean <- brfss.2014.small %>% 
  mutate(TRNSGNDR = recode_factor(.x = TRNSGNDR,
                                  `1` = 'Male to female',
                                  `2` = 'Female to male',
                                  `3` = 'Gender non-conforming'))
# Check your work
summary(object = brfss.clean)
```

Keep going: 

```{r}
# recode transgender, age, income, educ, health plan
brfss.clean <- brfss.2014.small %>% 
  mutate(TRNSGNDR = recode_factor(.x = TRNSGNDR,
                                  `1` = 'Male to female',
                                  `2` = 'Female to male',
                                  `3` = 'Gender non-conforming')) %>%
  mutate(X_AGEG5YR = recode_factor(.x = X_AGEG5YR,
                                  `5` = '40-44',
                                  `6` = '45-49',
                                  `7` = '50-54',
                                  `8` = '55-59',
                                  `9` = '60-64',
                                  `10` = '65-69',
                                  `11` = '70-74')) %>%
  mutate(X_INCOMG = recode_factor(.x = X_INCOMG,
                                  `1` = 'Less than $15,000',
                                  `2` = '$15,000 to less than $25,000',
                                  `3` = '$25,000 to less than $35,000',
                                  `4` = '$35,000 to less than $50,000',
                                  `5` = '$50,000 or more',
                                  `9` = 'Don\'t know/not sure/missing')) %>%
  mutate(X_EDUCAG = recode_factor(.x = X_EDUCAG,
                                  `1` = 'Did not graduate high school',
                                  `2` = 'Graduated high school',
                                  `3` = 'Attended College/Technical School',
                                  `4` = 'Graduated from College/Technical School',
                                  `9` = NA_character_)) %>%
  mutate(HLTHPLN1 = recode_factor(.x = HLTHPLN1,
                                  `1` = 'Yes',
                                  `2` = 'No',
                                  `7` = 'Don\'t know/not sure/missing',
                                  `9` = 'Refused')) 
```

```{r}
# Check your work
summary(object = brfss.clean)
```

Recoding `X_RACE` is a little tricker, let's start by looking at the variable in `brfss.clean`:

```{r}
# table of race variable
table(brfss.clean$X_RACE)
```

How do we translate this into the table categories? 

For `X_RACE` it looks like: 

- `1` in the data is `White` in the table 
- `2` in the data is `Black` in the table 
- `3` in the data is `Native American` in the table 
- `4` & `5` in the data are `Asian/Pacific Islander` in the table 
- `6`, `7`, `8`, & `9` in the data are `Other` in the table 

We can add this and the `HADMAM` coding (see page 37 in the codebook) to the data cleaning.

```{r}
# recoding with all variable labels
brfss.clean <- brfss.2014.small %>% 
  mutate(TRNSGNDR = recode_factor(.x = TRNSGNDR,
                                  `1` = 'Male to female',
                                  `2` = 'Female to male',
                                  `3` = 'Gender non-conforming')) %>%
  mutate(X_AGEG5YR = recode_factor(.x = X_AGEG5YR,
                                  `5` = '40-44',
                                  `6` = '45-49',
                                  `7` = '50-54',
                                  `8` = '55-59',
                                  `9` = '60-64',
                                  `10` = '65-69',
                                  `11` = '70-74')) %>%
  mutate(X_INCOMG = recode_factor(.x = X_INCOMG,
                                  `1` = 'Less than $15,000',
                                  `2` = '$15,000 to less than $25,000',
                                  `3` = '$25,000 to less than $35,000',
                                  `4` = '$35,000 to less than $50,000',
                                  `5` = '$50,000 or more',
                                  `9` = 'Don\'t know/not sure/missing')) %>%
  mutate(X_EDUCAG = recode_factor(.x = X_EDUCAG,
                                  `1` = 'Did not graduate high school',
                                  `2` = 'Graduated high school',
                                  `3` = 'Attended College/Technical School',
                                  `4` = 'Graduated from College/Technical School',
                                  `9` = NA_character_)) %>%
  mutate(HLTHPLN1 = recode_factor(.x = HLTHPLN1,
                                  `1` = 'Yes',
                                  `2` = 'No',
                                  `7` = 'Don\'t know/not sure/missing',
                                  `9` = 'Refused')) %>%
  mutate(X_RACE = recode_factor(.x = X_RACE, 
                                `1` = '',
                                `2` = '',
                                `3` = '',
                                `4` = '',
                                `5` = '',
                                `6` = '',
                                `7` = '',
                                `8` = '',
                                `9` = '')) %>%
  mutate(HADMAM = recode_factor(.x = HADMAM,
                                `1` = 'Yes',
                                `2` = 'No',
                                `7` = 'Don\'t know/not sure/missing',
                                `9` = 'Refused'))
```

```{r}
# check the recoding
summary(object = brfss.clean)
```

# Make the table 

- Use `tableone` to  make a table of all the variables 
- Check the table against the one we are reproducing 

```{r}
# make a table of all the variables in the data frame
CreateTableOne(data = brfss.clean)
```

# What went wrong?

- The transgender percentages are different 
- The race percentages are different 
- The overall n is different 

# What went wrong with the race variable?

**Native Hawaiians or other Pacific Islander** (category 5) category of `X_RACE` was coded as `Other` during recoding rather than as `Asian/Pacific Islander`.

```{r}
# recoding with variable labels
brfss.clean <- brfss.2014.small %>% 
  mutate(TRNSGNDR = recode_factor(.x = TRNSGNDR,
                                  `1` = 'Male to female',
                                  `2` = 'Female to male',
                                  `3` = 'Gender non-conforming')) %>%
  mutate(X_AGEG5YR = recode_factor(.x = X_AGEG5YR,
                                  `5` = '40-44',
                                  `6` = '45-49',
                                  `7` = '50-54',
                                  `8` = '55-59',
                                  `9` = '60-64',
                                  `10` = '65-69',
                                  `11` = '70-74')) %>%
  mutate(X_INCOMG = recode_factor(.x = X_INCOMG,
                                  `1` = 'Less than $15,000',
                                  `2` = '$15,000 to less than $25,000',
                                  `3` = '$25,000 to less than $35,000',
                                  `4` = '$35,000 to less than $50,000',
                                  `5` = '$50,000 or more',
                                  `9` = 'Don\'t know/not sure/missing')) %>%
  mutate(X_EDUCAG = recode_factor(.x = X_EDUCAG,
                                  `1` = 'Did not graduate high school',
                                  `2` = 'Graduated high school',
                                  `3` = 'Attended College/Technical School',
                                  `4` = 'Graduated from College/Technical School',
                                  `9` = NA_character_)) %>%
  mutate(HLTHPLN1 = recode_factor(.x = HLTHPLN1,
                                  `1` = 'Yes',
                                  `2` = 'No',
                                  `7` = 'Don\'t know/not sure/missing',
                                  `9` = 'Refused')) %>%
  mutate(X_RACE = recode_factor(.x = X_RACE, 
                                `1` = '',
                                `2` = '',
                                `3` = '',
                                `4` = '',
                                `5` = '',                
                                `6` = '',
                                `7` = '',
                                `8` = '',
                                `9` = '')) %>%
  mutate(HADMAM = recode_factor(.x = HADMAM,
                                `1` = 'Yes',
                                `2` = 'No',
                                `7` = 'Don\'t know/not sure/missing',
                                `9` = 'Refused'))
```

```{r}
# make a table of all the variables in the data frame
CreateTableOne(data = brfss.clean)
```

# What went wrong with the transgender variable and the sample size?

- The two "Refused" observations from `HADMAM` were removed from `TRNSGNDR` but were left in all other variables 
- Use `if_else()` to recode `TRNSGNDR` variable as `NA` for these two cases but leave all the other cases alone 

```{r}
# recoding with variable labels
# fixing recoding error and selecting variables in the table 
brfss.clean <- brfss.2014.small %>% 
  mutate(TRNSGNDR = recode_factor(.x = TRNSGNDR,
                                  `1` = 'Male to female',
                                  `2` = 'Female to male',
                                  `3` = 'Gender non-conforming')) %>%
  mutate(TRNSGNDR = if_else(condition = HADMAM != 9,     # HADMAM is not 9
                            true = TRNSGNDR,             # if true keep TRNSGNDR value
                            false = as.factor(NA))) %>%  # if false make NA
  mutate(X_AGEG5YR = recode_factor(.x = X_AGEG5YR,
                                  `5` = '40-44',
                                  `6` = '45-49',
                                  `7` = '50-54',
                                  `8` = '55-59',
                                  `9` = '60-64',
                                  `10` = '65-69',
                                  `11` = '70-74')) %>%
  mutate(X_INCOMG = recode_factor(.x = X_INCOMG,
                                  `1` = 'Less than $15,000',
                                  `2` = '$15,000 to less than $25,000',
                                  `3` = '$25,000 to less than $35,000',
                                  `4` = '$35,000 to less than $50,000',
                                  `5` = '$50,000 or more',
                                  `9` = 'Don\'t know/not sure/missing')) %>%
  mutate(X_EDUCAG = recode_factor(.x = X_EDUCAG,
                                  `1` = 'Did not graduate high school',
                                  `2` = 'Graduated high school',
                                  `3` = 'Attended College/Technical School',
                                  `4` = 'Graduated from College/Technical School',
                                  `9` = NA_character_)) %>%
  mutate(HLTHPLN1 = recode_factor(.x = HLTHPLN1,
                                  `1` = 'Yes',
                                  `2` = 'No',
                                  `7` = 'Don\'t know/not sure/missing',
                                  `9` = 'Refused')) %>%
  mutate(X_RACE = recode_factor(.x = X_RACE, 
                                `1` = 'White',
                                `2` = 'Black',
                                `3` = 'Native American',
                                `4` = 'Asian/Pacific Islander',
                                `5` = 'Other',
                                `6` = 'Other',
                                `7` = 'Other',
                                `8` = 'Other',
                                `9` = 'Other')) %>%
  select(TRNSGNDR, X_AGEG5YR, X_RACE,X_INCOMG, X_EDUCAG, HLTHPLN1)
```

```{r}
# make a table of all the variables in the data frame
CreateTableOne(data = brfss.clean)
```

Great! We reproduced the table! Here is the full code formatted with prolog. 

```{r}
# PROLOG   ################################################################

# PROJECT: NAME OF PROJECT HERE
# PURPOSE: MAJOR POINT(S) OF WHAT I AM DOING WITH THE DATA HERE
# DIR:     list directory(-ies) for files here
# DATA:    list dataset file names/availability here, e.g.,
#          filename.correctextention 
#          somewebaddress.com 
# AUTHOR:  AUTHOR NAME(S) 
# CREATED: MONTH dd, YEAR 
# LATEST:  MONTH dd, YEAR 
# NOTES:   indent all additional lines under each heading, 
#          & use the apostrophe hashmark bookends that appear  
#          KEEP PURPOSE, AUTHOR, CREATED & LATEST ENTRIES IN UPPER CASE, 
#          with appropriate case for DIR & DATA, lower case for notes 
#          If multiple lines become too much, 
#          simplify and write code book and readme. 

# PROLOG   ###############################################################

# make sure haven, tidyverse, tableone are installed 

# open the haven package to read an xpt
library(package = "haven")

# create a temporary file to store the zipped file
# before you open it
temp <- tempfile(fileext = ".zip")

# use download.file to put the zipped file in the temp file
# this will take a couple of minutes depending on computer speed
download.file(url = "http://www.cdc.gov/brfss/annual_data/2014/files/LLCP2014XPT.zip",
              destfile = temp)

# unzip it and read it
brfss.2014 <- read_xpt(file = temp)

# save it to data folder
write.csv(x = brfss.2014, file = "data/brfss_2014.csv", row.names = FALSE)

# import data 
brfss.2014 <- read.csv(file = "data/brfss_2014.csv")

# open tidyverse for data management
library(package = "tidyverse") 

# open tableone for making a table
library(package = "tableone")

# select variables and filter cases 
brfss.2014.small <- brfss.2014 %>% 
  select(TRNSGNDR, X_AGEG5YR, X_RACE, X_INCOMG,
         X_EDUCAG, HLTHPLN1, HADMAM) %>%
  filter(TRNSGNDR >= 1 & TRNSGNDR <= 3) %>%
  filter(X_AGEG5YR >= 5 & X_AGEG5YR <= 11) %>% 
  filter(!is.na(HADMAM))

# recoding with variable labels
# fixing recoding error and selecting variables in the table 
brfss.clean <- brfss.2014.small %>% 
  mutate(TRNSGNDR = recode_factor(.x = TRNSGNDR,
                                  `1` = 'Male to female',
                                  `2` = 'Female to male',
                                  `3` = 'Gender non-conforming')) %>%
  mutate(TRNSGNDR = if_else(condition = HADMAM != 9,     # HADMAM is not 9
                            true = TRNSGNDR,             # if true keep TRNSGNDR value
                            false = as.factor(NA))) %>%  # if false make NA
  mutate(X_AGEG5YR = recode_factor(.x = X_AGEG5YR,
                                  `5` = '40-44',
                                  `6` = '45-49',
                                  `7` = '50-54',
                                  `8` = '55-59',
                                  `9` = '60-64',
                                  `10` = '65-69',
                                  `11` = '70-74')) %>%
  mutate(X_INCOMG = recode_factor(.x = X_INCOMG,
                                  `1` = 'Less than $15,000',
                                  `2` = '$15,000 to less than $25,000',
                                  `3` = '$25,000 to less than $35,000',
                                  `4` = '$35,000 to less than $50,000',
                                  `5` = '$50,000 or more',
                                  `9` = 'Don\'t know/not sure/missing')) %>%
  mutate(X_EDUCAG = recode_factor(.x = X_EDUCAG,
                                  `1` = 'Did not graduate high school',
                                  `2` = 'Graduated high school',
                                  `3` = 'Attended College/Technical School',
                                  `4` = 'Graduated from College/Technical School',
                                  `9` = NA_character_)) %>%
  mutate(HLTHPLN1 = recode_factor(.x = HLTHPLN1,
                                  `1` = 'Yes',
                                  `2` = 'No',
                                  `7` = 'Don\'t know/not sure/missing',
                                  `9` = 'Refused')) %>%
  mutate(X_RACE = recode_factor(.x = X_RACE, 
                                `1` = 'White',
                                `2` = 'Black',
                                `3` = 'Native American',
                                `4` = 'Asian/Pacific Islander',
                                `5` = 'Other',
                                `6` = 'Other',
                                `7` = 'Other',
                                `8` = 'Other',
                                `9` = 'Other')) %>%
  select(TRNSGNDR, X_AGEG5YR, X_RACE,X_INCOMG, X_EDUCAG, HLTHPLN1)

# make a table of all the variables in the data frame
CreateTableOne(data = brfss.clean)

```

# More practice!

Add to the code to get even closer to the published version of the table...

- Use `rename()` to name the variables something more intuitive 
- Use the help documentation and online resources to keep formatting the table with better labels and other options 
- Check out other options for table formatting and try something other than `tableone` (e.g., `knitr`)


